%-------------------------------------------------------------------------------
%   SHREESHAIL SHIVPPA PADADALI — RESUME
%   LaTeX (XeLaTeX or pdfLaTeX), single-page, ATS-friendly.
%   Based on Jake Gutierrez's open-source resume template (MIT).
%
%   To compile on Overleaf:
%     1. Create a New Project -> Blank Project.
%     2. Replace main.tex with the contents of this file.
%     3. Click "Recompile" (default pdfLaTeX engine works).
%     4. Click the download (arrow) icon to save the PDF.
%-------------------------------------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%-------------------------------------------------------------------------------
%   PAGE GEOMETRY & STYLING
%-------------------------------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Make the PDF machine-readable (ATS-friendly).
\pdfgentounicode=1

%-------------------------------------------------------------------------------
%   CUSTOM COMMANDS
%-------------------------------------------------------------------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%===============================================================================
\begin{document}
%===============================================================================

%-------------------------------------------------------------------------------
%   HEADER
%-------------------------------------------------------------------------------
\begin{center}
    {\Huge \scshape Shreeshail Shivppa Padadali} \\ \vspace{2pt}
    \small Amaravati Gents PG, Brookfield, Bengaluru 560037 \\ \vspace{2pt}
    \small
    \faPhone\ +91-8277220852 \quad
    \faEnvelope\ \href{mailto:shreeshailx@gmail.com}{shreeshailx@gmail.com} \\ \vspace{4pt}
    \faGlobe\ \href{https://shreeshail-sp.github.io/Portfolio/}{Portfolio} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/shreeshail-padadali/}{LinkedIn} \quad
    \faGithub\ \href{https://github.com/Shreeshail-sp}{GitHub} \quad
    \faTrophy\ \href{https://www.kaggle.com/}{Kaggle}
\end{center}

%-------------------------------------------------------------------------------
%   CAREER OBJECTIVE
%-------------------------------------------------------------------------------
\section{Career Objective}
\small Motivated Computer Science undergraduate eager to take on real-world challenges and contribute meaningfully to impactful projects. Quick learner with a strong interest in building practical solutions and working in team-driven environments. Seeking an internship opportunity to grow, take ownership, and deliver high-quality results.

%-------------------------------------------------------------------------------
%   EDUCATION
%-------------------------------------------------------------------------------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {CMR Institute of Technology}{2022 -- 2026 \textit{(Expected)}}
    {B.E. \textit{(Computer Science and Engineering)}}{Bengaluru, Karnataka}

  \resumeSubheading
    {Ambika PU College}{2020 -- 2022}
    {Pre-University \textit{(Science)}}{Puttur, Karnataka}

  \resumeSubheading
    {Shri Sharada English Medium High School}{2019 -- 2020}
    {SSLC}{Muddebihal, Karnataka}

\resumeSubHeadingListEnd

%-------------------------------------------------------------------------------
%   TECHNICAL SKILLS
%-------------------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.0in, label={}]\small{\item{
    \textbf{Programming:} Python (NumPy, Pandas, OOP), C \\ \vspace{2pt}
    \textbf{Data Science \& Analysis:} Data Cleaning, Visualization (Matplotlib, Seaborn), EDA \\ \vspace{2pt}
    \textbf{Machine Learning:} Scikit-learn, Supervised \& Unsupervised Learning, Model Evaluation \\ \vspace{2pt}
    \textbf{NLP:} NLTK (Basics), Text Preprocessing, Tokenization, VADER \\ \vspace{2pt}
    \textbf{AI \& GenAI:} LLMs, RAG Pipelines, OpenAI APIs, LangChain, FAISS \\ \vspace{2pt}
    \textbf{DevOps \& Cloud:} Docker, Kubernetes, AWS ECS, Amazon ECR, IAM, CloudWatch, Terraform \\ \vspace{2pt}
    \textbf{Monitoring \& Observability:} Prometheus, Grafana, ELK Stack \\ \vspace{2pt}
    \textbf{CI/CD \& Tools:} Git, GitHub, GitHub Actions, Jenkins (Basic), Postman \\ \vspace{2pt}
    \textbf{Databases:} MySQL, SQL (Joins, Queries, Data Retrieval) \\ \vspace{2pt}
    \textbf{Soft Skills:} Communication, Client Interaction, Presentation, Teamwork, Leadership
}}\end{itemize}

%-------------------------------------------------------------------------------
%   EXPERIENCE
%-------------------------------------------------------------------------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {DevOps Intern -- Avijo}{Apr 2026 -- Present}
    {Internship}{Remote}
    \resumeItemListStart
        \resumeItem{Containerized backend applications using \textbf{Docker} and deployed services on \textbf{AWS ECS}.}
        \resumeItem{Built automated \textbf{CI/CD pipelines} with GitHub Actions and integrated \textbf{Amazon ECR} for deployments.}
        \resumeItem{Monitored deployments, tested APIs using Postman, and managed cloud services like \textbf{ECS, IAM, and CloudWatch}.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------------------------------------------
%   PROJECTS
%-------------------------------------------------------------------------------
\section{Projects}
\resumeSubHeadingListStart

  % --- Project 1: AI-powered Scalable MLOps Platform ---
  \resumeProjectHeading
    {\textbf{AI-powered Scalable MLOps Platform} \emph{$|$ Python, FastAPI, Docker, Kubernetes, Terraform, GitHub Actions} \\
     \footnotesize \faGithub\ \href{https://github.com/Shreeshail-sp/AI-powered-Scalable-MLOps-Platform}{GitHub Repository}}{2025}
    \resumeItemListStart
      \resumeItem{Designed and built an end-to-end \textbf{MLOps automation platform} that takes a Git push from commit to live, scaled, monitored ML API on Kubernetes -- with zero manual steps.}
      \resumeItem{Provisioned cloud infrastructure (VPC, ECR, EKS) using \textbf{Terraform} and authored a multi-stage \textbf{Dockerfile} producing a $\sim$250 MB non-root image with health probes baked in.}
      \resumeItem{Authored Kubernetes manifests with HPA (auto-scale 2-10 pods on CPU/memory), rolling updates, readiness/liveness probes, and Kustomize overlays for dev/staging/prod environments.}
      \resumeItem{Built CI/CD with \textbf{GitHub Actions}: ruff lint + pytest matrix (91\% coverage), Docker build with cache, image publish to GHCR, automated rollout with rollback on smoke-test failure.}
    \resumeItemListEnd

  % --- Project 2: Airbnb Sentiment Analysis (NOW WITH LIVE DEMO) ---
  \resumeProjectHeading
    {\textbf{Airbnb Sentiment Analysis} \emph{$|$ Python, NLTK (VADER), Pandas, Plotly, GitHub Pages} \\
     \footnotesize \faGlobe\ \href{https://shreeshail-sp.github.io/Air_BNB_Sentiment-_Ananlysis/}{Live Demo} \quad
     \faGithub\ \href{https://github.com/Shreeshail-sp/Air_BNB_Sentiment-_Ananlysis}{GitHub Repository}}{2024}
    \resumeItemListStart
      \resumeItem{Built an end-to-end NLP pipeline that ranks \textbf{119 Airbnb listings} across \textbf{14{,}579 reviews} by sentiment using VADER and POS-tagged noun-phrase mining, surfacing features guests praise or complain about.}
      \resumeItem{Shipped a public, fully static dashboard on \textbf{GitHub Pages} with sortable rankings, distribution charts, and four interactive Plotly reports -- requires no backend server.}
      \resumeItem{Reduced report HTML payloads from 4.5 MB to 9 KB each (\textbf{500$\times$ smaller}) by switching from inlined plotly.js to CDN, making the dashboard load instantly.}
    \resumeItemListEnd

  % --- Project 3: FinBot ---
  \resumeProjectHeading
    {\textbf{FinBot: News Research Tool} \emph{$|$ Python, LangChain, FAISS, OpenAI, Streamlit} \\
     \footnotesize \faGithub\ \href{https://github.com/Shreeshail-sp}{GitHub Profile}}{2024 -- 2025}
    \resumeItemListStart
      \resumeItem{Built an LLM-powered financial news research system implementing \textbf{retrieval-augmented generation} to surface accurate, source-backed answers for analysts.}
      \resumeItem{Developed ingestion pipelines with advanced text splitting and OpenAI embeddings; implemented \textbf{FAISS} vector index for sub-second semantic retrieval.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------------------------------------------
%   CO-CURRICULAR & LEADERSHIP
%-------------------------------------------------------------------------------
\section{Co-Curricular \& Leadership}
\begin{itemize}[leftmargin=0.0in, label={}]\small{\item{
    \textbf{Certifications:} Prompt Engineering, Columbia University, May 2025 \\ \vspace{2pt}
    \textbf{Industrial Visits:} Attended \textbf{Bangalore Tech Summit 2024} to explore AI, Cloud, and Data Engineering industry trends. \\ \vspace{2pt}
    \textbf{Extracurriculars:} Active \textbf{Cricket} and \textbf{Volleyball} player -- demonstrates teamwork, discipline, and leadership. \\ \vspace{2pt}
    \textbf{NSS Volunteer:} Organized digital literacy drives and exam-awareness sessions; led coordination and communications with local stakeholders.
}}\end{itemize}

%===============================================================================
\end{document}
%===============================================================================
